---
title: "charity-analysis"
subtitle:"version_004"
author: "PotapenkoEugene"
date: "2022-12-20"
output: html_document
---

# Library install
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load preprocessed data
source("CharityHospital_R_2022-11-02_1448.R")

if(!require('Hmisc')) install.packages('Hmisc') ; library(Hmisc)
if(!require('tidyverse')) install.packages('tidyverse') ; library(tidyverse)
if(!require('data.table')) install.packages('data.table') ; library(data.table)
if(!require('dplyr')) install.packages('dplyr') ; library(dplyr)
if(!require('magrittr')) install.packages('magrittr') ; library(magrittr)
if(!require('eeptools')) install.packages('eeptools') ; library(eeptools)
if(!require('naniar')) install.packages('naniar') ; library(naniar)
if(!require('fastDummies')) install.packages('fastDummies') ; library(fastDummies)
if(!require('forcats')) install.packages('forcats') ; library(forcats)

if(!require('wesanderson')) install.packages('wesanderson') ; library(wesanderson)
if(!require('RColorBrewer')) install.packages('RColorBrewer') ; library(RColorBrewer)

if(!require('ggpubr')) install.packages('ggpubr') ; library(ggpubr)
if(!require('grid')) install.packages('grid') ; library(grid)
if(!require('gridExtra')) install.packages('gridExtra') ; library(gridExtra)
if(!require('ggplotify')) install.packages('ggplotify') ; library(ggplotify)
if(!require('ggmosaic')) install.packages('ggmosaic') ; library(ggmosaic)
if(!require('ggpol')) install.packages('ggpol') ; library(ggpol)
if(!require('plotly')) install.packages('plotly') ; library(plotly)
if(!require('ggplot2')) install.packages('ggplot2') ; library(ggplot2)

#if(!require('shiny')) install.packages('shiny') ; library(shiny)

```

# Functions
```{r}
### FUNC
doc_vars_mutate <-
  function(df, col.bool, col.reason){
  df %>%
    dplyr::rename(target.bool = !!col.bool, target.reason = !!col.reason) %>%
    # Move some values from "bool" to reason
    dplyr::mutate(target.reason = as.factor(case_when(target.bool == 'восстанавливает' ~ target.bool,
                                            target.bool == 'заложен' ~ target.bool,
                                            TRUE ~ target.reason))) %>%
    # "bool" to bool
    dplyr::mutate(target.bool = as.factor(case_when(target.bool %in% c('есть') ~ T,
                                          target.bool %in% c('восстанавливает',
                                                               'заложен',
                                                               'нет')~ F,
                                          target.bool == 'нет данных' ~ NA))) %>%
    dplyr::rename_with(~ c(col.bool, col.reason), all_of(c('target.bool', 'target.reason')))
  }

sum_rowwise_vars <- 
  function(df, prefix, NAstring){
      df %>%
        dplyr::filter(is.na(redcap_repeat_instance)) %>% # keep only info rows of records
        dplyr::select(record_id, starts_with(prefix)) %>%
        dplyr::mutate_at(vars(starts_with(prefix)), function(x) na_if(x, NAstring)) %>% # replace ОТРИЦАЕТ with NA
        # Calculate number of ch ds per patient
        dplyr::mutate_at(vars(starts_with(prefix)), function(x) ifelse(!is.na(x), T, F)) %>%
        rowwise() %T>% 
        {varname <<- paste0(prefix, '.number')} %>% # save new varname
        mutate(!!varname := sum(cur_data()) - record_id) %>% # just minus record_id (simpliest way)
        dplyr::select(!!varname)
        
  }

first_last_dinamics <- function(vec){
      combinations <-
        vec %>%
          str_split(., '\\|') %>%
          do.call(c, .) %>% 
          unique %>%
          .[. != 'NA'] %>% # drop NA
          c(., .) %>%
          combn(2) %>% 
          t %>%
          as.data.frame %>% 
          unique %>%
          rowwise() %>%
          dplyr::mutate(Rangs = paste0(V1, ' -> ', V2)) %>%
          .$Rangs
          
      
      vec %>%
        str_split(., '\\|') %>%
        sapply(function(x) {
          x = x[x != 'NA']
          if(length(x) == 0) {
            return(NA)
            } else{
              x = ifelse(x[1] == x[length(x)],
                                   x[1],
                                   paste0(x[1], ' -> ', x[length(x)]))
            }
        }
          )
}

most_frequent_dinamics <- function(vec){
        vec %>%
        str_split(., '\\|') %>%
        sapply(function(x) {
          x = x[x != 'NA']
          if(length(x) == 0) {
            return(NA)
          }else{
            median(x)
          }
          })
}

# Машина функция
get_one_var_hist <- function(data, var, out_dir, xtitle,
                             pall_values, height, width,
                             ytitle='Количество человек',
                             ratio=0.2) {
  if (!dir.exists(out_dir)) {
    dir.create(out_dir, recursive = T)
  }
  df <- data.frame(table(data[[var]])) %>%
    magrittr::set_colnames(c('condition', 'counts'))
  y_lim <- plyr::round_any(max(df$counts) + 100, 100)
  plot_title <- sprintf('%s (%d/%d -- есть информация, %d/%d -- NAs)',
                        xtitle, sum(df$counts), nrow(data),
                        sum(is.na(data[[var]])), nrow(data))
  plt <- ggplot(df, aes(x = reorder(condition, counts), y = counts, fill=condition))+
    geom_bar(stat = 'identity')+
    geom_text(aes(label = counts), vjust = 0, size=4.5)+
    theme_bw(base_size=11)+
    ylab(ytitle)+
    xlab(xtitle)+
    ggtitle(plot_title)+
    ylim(0, y_lim)+
    scale_fill_manual(values=pall_values)+
    theme(legend.text.align = 0, legend.key.size=unit(0.2, "in"),
          legend.text = element_text(size=13),
          aspect.ratio = ratio, legend.position = 'right',
          legend.title = element_blank(),
          plot.margin=grid::unit(c(0,0,0,0), "in"),
          axis.text.x = element_text(angle = 45, hjust=1),
          plot.title = element_text(hjust = 0.5))
  ggsave(plt, filename = sprintf('%s/%s_bar_plot.png', out_dir, var),
         height = height, width = width)
  plt
}

```

# Postprocessing
```{r}
data <-
  data %>%
  # Rename some vars
  dplyr::rename(Observation = redcap_repeat_instrument.factor) %>% 
  # Drop useless vars 
  dplyr::select(-(starts_with('complaint_lite') & ends_with('.factor'))) %>%
  # Split some vars
  separate(id_status.factor, into = c('id_status.factor.bool', 'id_status.factor.reason'), sep = '/') %>% 
  separate(oms_status.factor, into = c('oms_status.factor.bool', 'oms_status.factor.reason'), sep = '/') %>% 
  separate(sn_status.factor, into = c('sn_status.factor.bool', 'sn_status.factor.reason'), sep = '/') %>%
  # Mutate docs vars
  doc_vars_mutate('id_status.factor.bool', 'id_status.factor.reason') %>%
  doc_vars_mutate('oms_status.factor.bool', 'oms_status.factor.reason') %>%
  doc_vars_mutate('sn_status.factor.bool', 'sn_status.factor.reason') %>%
  # Encode homeless
  dplyr::mutate(Homeless = case_when(where_homless %in%  c(1, 14, 16, 6, 11) ~ 'уличный',
                                     where_homless %in% c(17, 2, 3, 4, 12, 5, 15, 7) ~ 'условно уличный',
                                     where_homless %in% c(8, 9, 13) ~ 'домашний', 
                                     where_homless == 10 | is.na(where_homless) ~ as.character(NA))) %>%
  dplyr::mutate(smp = case_when(trimws(place) %in% c('14 городская больница', '36 ГБ', '40', '40 ГБ, Сестрорецк', 'александровская больница', 'Боткина, уже там, старая', 'ГБ 14', 'ГБ 40', 'ГБ №3', 'ГБ №40', 'Георгия', 'ГКБ №40', 'Джанелидзе', 'Мариинская больница 5  отд. 11 палата', 'Покровская больница', 'Попытка госпитализации в ГНБ. Отказ от госпитализации по причине отсутствия прожарки и справки БОМЖ. В приёмном покое ГНБ у пациента возникли судороги. Вызвана скорая помощь, доставлен Александровскую больницу', 'СМП', 'Смп 78 Леванеев бригада,Джа', 'Травма по 55 гп 112 СМП', 'НИИ кардиологии им Алмазова', 'отказ от госпитализации') ~ T,
                                is.na(place) ~ NA,
                                T ~ F))
```

# EDA
```{r}
# Look on lethal cases
data$ds[grepl('смерть|летальный', data$ds, ignore.case = T)] # only 4 cases

# chatGPT decoding of diagnosis in ICD-10 code
if(F){ # skip by default
  # DS
  ds <- data$ds %>% unique %>% na.omit %>% gsub('\n', ' ', .) %>% head(100)
  library(gptchatteR)
  # Auth
  key = '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'
  chatter.auth(key)
  # Create chat
  chatter.create()
  # Chatting!
  context = 'Раздели составные врачебные диагнозы написанные в свободном стиле на отдельные диагнозы и переведи их в классификацию по МКБ-10. Ответ запиши в виде кодов МКБ-10 перечисленных через запятую. При невозожности определения диагноза к одной из классификаций МКБ-10, заполни значением NA'
  chatter.feed(context)
  
  chunks = seq(from = 20, to = length(ds), by = 20)
  answers.list <-
    lapply(1:length(chunks), function(i){
    if(i==1){
      start = 1
      end = chunks[i]
    } else{
      start = chunks[i-1] + 1
      end = chunks[i]
    }
      answer = chatter.chat(ds[start:end],return_response = T, feed = F)
      Sys.sleep(3)
      return(answer$choices)
  })
  
  
  ds.df <- data.frame(Diagnos = ds)
  answers.list %>%
    do.call(rbind, .) %>%
    cbind(ds.df, .) %>%
    dplyr::mutate(text = gsub('\n', '', trimws(text))) %>%
    write.xlsx('Decoding_diagnosis.xlsx')
  }
```

# Classified vars
```{r}
# Base vars:
base_vars.factor = c('gender.factor', 'age.group',
              # Docs
              'id_status.factor.reason', 'oms_status.factor.reason', 'sn_status.factor.reason',
              # Additctions
              'nicotin.factor', 'alcogolic.factor', 'narco.factor', 'ne_narco.factor')

base_vars.bool = c('id_status.factor.bool', 'oms_status.factor.bool', 'sn_status.factor.bool')

quant_vars = c('ObsNum', 'age.actual')


# Dummy variables:
dummy_vars_raw = c('Observation', 'Homeless',
               'ds_icd_1.factor', 'ds_icd_2.factor', 'ds_icd_3.factor', 
               'etest_hiv.factor', 'etest_hbsag.factor', 'etest_hcv.factor', 'etest_lues.factor', 'etest_covid19.factor')
dummy_vars_already <- c('complaint_lite')

# Dinamic variables
dinamic_vars = c('Observation', 'Homeless', 'alc_status.factor', 'smp')
```

# Transform data
```{r warning = F}
## Transform BirthDate to actual age (26.11.2022)
data$age.actual[!is.na(data$date_bd)] <- 
  age_calc(as.Date(data$date_bd[!is.na(data$date_bd)]),
           Sys.Date(),
           units = 'years') %>%
  floor

# Age group
data <-
  data %>%
  dplyr::mutate(
    age.group = case_when(
      age.actual < 18 ~ "<18 (несовершеннолетние)",
      age.actual >= 18 & age.actual < 45 ~ "18-44 (молодой возраст)",
      age.actual >= 45 & age.actual < 60 ~ "45-59 (средний возраст)",
      age.actual >= 60 & age.actual < 75 ~ "60-74 (пожилой возраст)",
      age.actual >= 75 ~ "75+ (старческий возраст)"
    )
  )
data$age.group <- factor(data$age.group, levels = sort(unique(data$age.group)))
```


# Processing of each type of vars
```{r warning=F}
# Dinamic vars (should be processed before dummy)
dinamic <-
  data %>%
    dplyr::select(record_id, dinamic_vars) %>%
    dplyr::group_by(record_id) %>%
    dplyr::summarise_all(function(x) paste(x, collapse = '|'))
## First - last
dinamic_firstlast <-
    dinamic %>%
    dplyr::rename_all(function(x) ifelse(x != 'record_id', paste0(x, '.dinamic'), x)) %>%
    dplyr::mutate_at(vars(ends_with('.dinamic')), 
                     function(x) first_last_dinamics(x) %>% replace_na('Нет данных') %>% as.factor)
## Most frequent
dinamic_mostfreq <-
    dinamic %>%
    dplyr::rename_all(function(x) ifelse(x != 'record_id', paste0(x, '.mostfreq'), x)) %>%
    dplyr::mutate_at(vars(ends_with('.mostfreq')), 
                     function(x) most_frequent_dinamics(x) %>% replace_na('Нет данных') %>% as.factor)
## Merge
data_dinamic <- left_join(dinamic_firstlast, dinamic_mostfreq, by = 'record_id')

# Renew names of dinamic vars with dinamic suffix
dinamic_vars = c(paste0(dinamic_vars, '.dinamic'),
                 paste0(dinamic_vars, '.mostfreq'))

# Proccess dummy vars (drop original dummy vars)
data_dummy <-
  data %>%
  dummy_cols(remove_first_dummy = F, ignore_na = T,
             select_columns = dummy_vars_raw) %>%
  dplyr::select(-dummy_vars_raw) %>% # remove original vars
  # Rename dummy vars already (for further join with original df)
  dplyr::rename_at(vars(starts_with(dummy_vars_already)), ~paste0('.',.)) %>%
  dplyr::select(record_id, starts_with(c(dummy_vars_raw, paste0('.', dummy_vars_already)), ignore.case = F)) %>% # select new vars + already dumm vars
  dplyr::group_by(record_id) %>%
  dplyr::summarise_all(function(x) sum(x, na.rm =T)) %>%
  dplyr::ungroup() %>%
  dplyr::select_if(function(x) sum(x, na.rm = T) != 0) # drop zero sum
# Add new dummied variables to list of quant vars
dummy_quant_vars = data_dummy %>% colnames %>% .[-1] # drom record_id

# Process quantative vars (among observation)
data_collapse <-
  data %>%
    dplyr::group_by(record_id) %>%
    dplyr::summarise(ObsNum = ifelse(n() == 1, 1, n() - 1))

# Rowwise vars
data_rowwise <- 
  data %>%
  dplyr::filter(is.na(Observation)) %>% # Keep only informative rows
  dplyr::select(record_id) %>%
  cbind(sum_rowwise_vars(data, 'ch_ds', 'отрицает')) # bind ID with rowwise vars

# Add rowwise new variables to quant
quant_vars = c(quant_vars, data_rowwise %>% dplyr::select(ends_with('.number')) %>% colnames)
```


# Basic stats
```{r}
selected_vars <- c(base_vars.bool, base_vars.factor, quant_vars, dummy_quant_vars, dinamic_vars)
##
data_done <-
  data %>%
  # filter out rows without base info
  dplyr::filter(is.na(redcap_repeat_instrument)) %>% 
  # Join with summed dummy vars
  right_join(data_dummy, by = 'record_id') %>%
  # Join with quant vars
  right_join(data_collapse, by = 'record_id') %>%
  # Join with rowwise vars
  right_join(data_rowwise, by = 'record_id') %>% 
  # Join with dinamic vars
  right_join(data_dinamic, by = 'record_id') %>%
  dplyr::select(record_id, all_of(selected_vars))
```

# HandMade analyses

## AgeGender
```{r fig.width=8}

ggGender1 <-
  data_done %>%
  dplyr::filter(!is.na(gender.factor) & !is.na(age.group)) %>%
  dplyr::group_by(age.group, gender.factor) %>%
  count %>%
  ggplot(aes(n, fct_rev(age.group), fill = gender.factor )) +
  geom_bar(stat = 'identity', position = 'dodge') +
  labs(x = 'Patients', y = 'Age group', fill = 'Gender') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(3,4)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
ggGender1

ggGender2 <-
  data_done %>%
  dplyr::mutate(age.bins = cut(data_done$age.actual, 15),
                count = 1) %>%
  dplyr::select(age.bins, count, gender.factor) %>%
  aggregate(count ~ gender.factor + age.bins, data = ., length) %>%
  dplyr::mutate(count = ifelse(gender.factor == 'мужской', count * -1, count)) %>%
  #Plot
  ggplot(aes(age.bins, count, fill = gender.factor)) +
  geom_bar(stat = 'identity') +
  facet_share(~gender.factor, dir = 'h', scales = 'free', reverse_num = T) +
  coord_flip() +
  labs(y = 'Age', x = 'Patients', fill = 'Sex') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(3,4)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        strip.text.x = element_text(face = 'bold', size = 14))
ggGender2

## gender (by Masha)

get_one_var_hist(data=data, var='gender.factor', out_dir='plots',
                 xtitle='Пол', pall_values=wes_palettes$BottleRocket2,
                 height = 2.5, width = 6)

```

## Home

### Home overall
```{r}
data %>%
  dplyr::filter(!is.na(redcap_repeat_instrument)) %>%
  dplyr::select(record_id, redcap_repeat_instrument, Homeless) %>%
  dplyr::summarise(Count = table(Homeless, exclude = NULL),
                   Homeless = names(table(Homeless, exclude = NULL))) %>%
  dplyr::mutate(Homeless = case_when(is.na(Homeless) ~ 'Нет данных',
                                     T ~ Homeless)) %>%
  # Plot 
  ggplot(aes(Count, fct_reorder(Homeless, Count) , fill = Homeless)) +
  geom_bar(stat = 'identity') +
  scale_fill_manual(values = wes_palettes$Rushmore1[2:5]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12),
        legend.position = 'none') +
  labs(x  = 'Observation', y = 'Home status')

```

# Documents: passport, OMS, SNILS
```{r}

a <- get_one_var_hist(data=data, var='sn_status.factor', out_dir='plots',
                      xtitle='Наличие СНИЛСа', pall_values=wes_palettes$Rushmore1,
                      height = 4, width = 9)
b <- get_one_var_hist(data=data, var='id_status.factor', out_dir='plots',
                      xtitle='Наличие паспорта', pall_values=wes_palettes$Rushmore1,
                      height = 4, width = 9)
c <- get_one_var_hist(data=data, var='oms_status.factor', out_dir='plots',
                      xtitle='Наличие ОМС', pall_values=wes_palettes$Rushmore1,
                      height = 4, width = 9)

abc_stacked <- ggpubr::ggarrange(a, b, c, nrow = 3, common.legend = T)
ggsave(abc_stacked, filename = 'plots/sn_id_oms_stacked.png', height = 10, width = 11)

```

### Home by Patients
```{r fig.width=8}
ggHome <-
  data_done %>%
  dplyr::filter(!is.na(Homeless.dinamic)) %>%
  dplyr::group_by(Homeless.dinamic) %>%
  count %>% 
  ggplot(aes(n, fct_reorder(Homeless.dinamic, desc(n)))) +
  geom_bar(stat = 'identity') +
  # Appereance
  labs(x = 'Patients', fill = 'Age group', y = 'Home status') +
  scale_fill_manual(values = rev(wes_palettes$Rushmore1)) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
ggHome


# Parlament plot
df_count <-
  data_done %>%
  dplyr::filter(!is.na(Homeless.dinamic)) %>%
  dplyr::group_by(Homeless.dinamic) %>%
  count %>%
  dplyr::mutate(Homeless.dinamic = as.character(Homeless.dinamic)) %>%
  dplyr::arrange(desc(n))

# Plot
ggplot(df_count) +
  geom_parliament(aes(seats = n, fill = Homeless.dinamic)) +
  scale_fill_manual(values = c('darkgrey', 
                               "black", "blue", "lightblue", "yellow", 
                               "red","purple", "green",
                               'orange', 'tomato4'), 
                    labels = df_count$Homeless.dinamic) +
  coord_fixed() + 
  labs(fill = 'Home status') +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12)) +
  theme_void()
``` 


## AgeAlcoNarco
```{r fig.width=14, message = F, warning = F}

data_done %>%
  dplyr::select(Homeless.mostfreq, nicotin.factor, alcogolic.factor, narco.factor, ne_narco.factor) %>%
  # dplyr::filter(!is.na(age.group)) %>%
  dplyr::group_by(Homeless.mostfreq) %>%
  dplyr::summarise(answer = names(table(alcogolic.factor)), # all factors - same value and order
                   Алкоголь = table(alcogolic.factor),
                   Никотин = table(nicotin.factor),
                   `ПАВ\nинъекционно`= table(narco.factor),
                   `ПАВ\nнеинъекционно` = table(ne_narco.factor)
                   ) %>%
  dplyr::ungroup() %>%
  melt %>%
  dplyr::mutate(value = as.numeric(value))  %>%
  dplyr::group_by(Homeless.mostfreq) %>% dplyr::mutate(Sum = sum(value)) %>% dplyr::ungroup() %>%
  #Plot  
  ggplot(aes(value, answer, fill = factor(Homeless.mostfreq, 
                                          levels = c('уличный',
                                                     'условно уличный',
                                                     'домашний',
                                                     'Нет данных')))) +
  geom_bar(stat = 'identity') +
  facet_grid(cols = vars(variable)) +
  # Appereance
  labs(x = 'Количество пациентов', y = 'Ответ', fill = 'Бездомность') +
  scale_fill_manual(values = c(wes_palettes$Rushmore1[3:4],
                               wes_palettes$BottleRocket2[c(1,2)])) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 18),
        legend.title = element_text(face = 'bold', size = 18),
        axis.text = element_text(size = 16, face = 'bold'),
        legend.text = element_text(size = 18),
        strip.text.x = element_text(face = 'bold', size = 18))

# Link with Home status(mostfreq)

data_done %>%
  dplyr::select(alcogolic.factor, Homeless.mostfreq) %>%
  dplyr::mutate(alcogolic.factor = alcogolic.factor %>% as.character %>% replace_na('Нет данных') %>% as.factor) %>%
  dplyr::filter(Homeless.mostfreq != 'Нет данных' &
                alcogolic.factor != 'Нет данных') %>%
  dplyr::mutate(alcogolic.factor = factor(alcogolic.factor, 
                                          levels = c('отрицает/отказ от ответа',
                                                     'избавился/был зависим',
                                                     'есть в настоящее время')),
                Homeless.mostfreq = factor(Homeless.mostfreq,
                                           levels = c('уличный',
                                                      'условно уличный',
                                                      'домашний'))) %>%
  # Plot
      ggplot() +
        geom_mosaic(aes(x = product(alcogolic.factor, 
                                    Homeless.mostfreq)), 
                    fill = wes_palettes$Rushmore1[3]) +
        geom_mosaic_text(aes(x = product(alcogolic.factor, 
                                    Homeless.mostfreq), label = after_stat(.wt)), as.label=TRUE) +
      theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12, face = 'bold'),
        legend.text = element_text(size = 12),
        strip.text.x = element_text(face = 'bold', size = 14)) +
  labs(y = 'Алкогольная зависимость',
       x = 'Статус бездомности')


data_done %>%
  dplyr::select(Homeless.mostfreq, alcogolic.factor, nicotin.factor, narco.factor, ne_narco.factor) %>%
  na_if('Нет данных') %>% # not take into account 
  # na_if('есть в настоящее время') %>% # for narco
  dplyr::mutate_all(as.character) %T>%
  {alco <<- chisq.test(.$Homeless.mostfreq, .$alcogolic.factor)} %T>%
  {nicotin <<- chisq.test(.$Homeless.mostfreq, .$nicotin.factor)} %T>%
  {narco <<- chisq.test(.$Homeless.mostfreq, .$narco.factor)} %T>%
  {ne_narco <<- chisq.test(.$Homeless.mostfreq, .$ne_narco.factor)} %>%
  invisible() # not to show the df

paste0('alco: ',alco$p.value)
paste0('nicotin: ', nicotin$p.value)
paste0('narco: ', narco$p.value)
paste0('ne_narco: ', ne_narco$p.value)
```


# Citizenship
```{r}
data$citizen.factor %>% 
  table %>%
  .[. != 0] %>%
  as.data.frame %>% setNames(c('Answer', 'Freq')) %>%
  ggplot(aes(Freq, fct_reorder(Answer, Freq))) +
  geom_bar(stat = 'identity') +
  theme_bw() +
  labs(x = 'Patients', y = 'Answer') + 
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))

data$citizen.factor %>% table %>% .[. != 0]


## citizenship (by Masha)

get_one_var_hist(data=data %>%
                   filter(`citizen.factor` != 0) %>%
                   mutate(`citizen.factor` = as.character(`citizen.factor`)),
                 var='citizen.factor', out_dir='plots',
                 xtitle='Гражданство', pall_values=c(wes_palettes$Rushmore1, wes_palettes$GrandBudapest1,
                                                     wes_palettes$GrandBudapest2),
                 height = 6, width = 8, ratio=0.8)
```

## Social diseases
```{r}
# Можно добавить какие-то переменные:

# only in one fiela (is.na(redcap_repeat_instrument) == T):
soc_ds.answer = c('hiv_1.factor', 'hb_1.factor', 'hc_1.factor', 'lues.factor', 'artv.factor') 
# Could be in each observation:
soc_ds.test = c('etest_hiv.factor', 'etest_hbsag.factor', 'etest_hcv.factor', 
                'etest_lues.factor', 'etest_covid19.factor') 

data_test_dinamic <-
  data %>%
  dplyr::select(record_id, soc_ds.test) %>%
  na_if('не тестировался') %>% # replace "не тестировался" на NA
  group_by(record_id) %>%
    # remove all NAs, separeate each test result for each patients by "|"
  dplyr::summarise_all(function(x) ifelse(all(is.na(x)), NA, paste(x[!is.na(x)], collapse = '|'))) %>%
  dplyr::mutate_at(vars(starts_with('etest')), first_last_dinamics)
    # Patients for checking (hiv):   
    # 1174 ++
    # 245 -- 
    # 1333 -+
  
# Join with answer
data %>%
    dplyr::filter(is.na(redcap_repeat_instrument)) %>% # keep only informative fields
    dplyr::select(record_id, soc_ds.answer) %>%
    left_join(data_test_dinamic, by = 'record_id') %>%
  #TODO
  dplyr::filter(record_id %in% c(245, 1174, 1333)) #TEMP checking:
```

## Social diseases plots
```{r}
data_soc_ds <-
  data %>%
  dplyr::filter(is.na(redcap_repeat_instrument)) %>% # take only informative fields
  dplyr::select(record_id, soc_ds.answer) %>%
  left_join(data_test_dinamic, by = 'record_id')

# Про ВИЧ

# Протестировано 170 человек, из них 152 (-), 
# 15 (+) (из них 2 не знали о своем статусе - осв 87% (в россии вроде как перевалила за 90 в среднем)), 
# 2 неопределенных, 1 - сероконверсия (тоже не знал(?))



just_hiv <- data_soc_ds %>%
  filter(!is.na(etest_hiv.factor) & !is.na(hiv_1.factor)) %>%
  select(etest_hiv.factor, hiv_1.factor, artv.factor)

hiv_plot <-
  just_hiv %>%
  ggplot(aes(x = hiv_1.factor, fill = etest_hiv.factor )) +
  geom_bar() +
  labs(x = 'Данные опроса', y = 'Количество', fill = 'Результат экспресс-тестирования') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(2, 3,4,5)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        legend.text = element_text(size = 12))
hiv_plot

# Ниже код для сохранения рисунков
# png(filename="ВИЧ.png", width = 750, height = 500)
# plot(hiv_plot)
# dev.off()

# table(just_tests$etest_hiv.factor)

# Про гепатит В

# протестировано 143 человека, из них 4 (+), 1 неопределенный, 138 (-)
# 2 людей не знали о своем статусе

just_hb <- data_soc_ds %>%
  filter(!is.na(etest_hbsag.factor) & !is.na(hb_1.factor)) %>%
  select(etest_hbsag.factor, hb_1.factor)

# table(just_hb$hb_1.factor)
# table(just_hb$etest_hbsag.factor)

hb_plot <-
  just_hb %>%
  ggplot(aes(x = hb_1.factor, fill = etest_hbsag.factor )) +
  geom_bar(width = 0.5) +
  labs(x = 'Данные опроса', y = 'Количество', fill = 'Результат экспресс-теста') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(3,4,5)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 18),
        legend.title = element_text(face = 'bold', size = 16),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.position = "none")
hb_plot

# library(ggbubr)
# library(grid)
# library(cowplot)

legend <- get_legend(hb_plot)
grid.newpage()                              

# Draw Only legend 
grid.draw(legend)

# png(filename="ВГВ.png", width = 750, height = 750)
# plot(hb_plot)
# dev.off()

# Про гепатит С

# Протестировано 133 человека, из них 17 (+), 1 неопределенный, 115 (-)
# 5 человек не знали о своем статусе

just_hc <- data_soc_ds %>%
  filter(!is.na(etest_hcv.factor) & !is.na(hc_1.factor)) %>%
  select(etest_hcv.factor, hc_1.factor)

hc_plot <-
  just_hc %>%
  ggplot(aes(x = hc_1.factor, fill = etest_hcv.factor )) +
  geom_bar(width = 0.5) +
  labs(x = 'Данные опроса', y = 'Количество', fill = 'Результат экспресс-теста') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(3,4,5)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 18),
        legend.title = element_text(face = 'bold', size = 16),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.position = "none") # +
  # geom_text(stat = "count", 
           # aes(label = after_stat(count)), vjust = 0.5)
hc_plot

# png(filename="ВГC.png", width = 750, height = 750)
# plot(hc_plot)
# dev.off()

# Про сифилис

# один случай сероконверсии, проведено 148 тестов

just_lues <- data_soc_ds %>%
  filter(!is.na(etest_lues.factor) & !is.na(lues.factor)) %>%
  select(etest_lues.factor, lues.factor)

table(just_lues$lues.factor)
table(just_lues$etest_lues.factor)

lues_plot <-
  just_lues %>%
  ggplot(aes(x = lues.factor, fill = etest_lues.factor )) +
  geom_bar(width = 0.5) +
  labs(x = 'Данные опроса', y = 'Количество', fill = 'Результат экспресс-теста') +
  scale_fill_manual(values = wes_palettes$Rushmore1[c(3,4,5)]) +
  theme_bw() +
  theme(axis.title = element_text(face = 'bold', size = 18),
        legend.title = element_text(face = 'bold', size = 16),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 14),
        legend.position = "none") # +
#  geom_text(stat = "count", 
 #           aes(label = after_stat(count)), vjust = -1)
lues_plot

# png(filename="сиф.png", width = 750, height = 750)
# plot(lues_plot)
# dev.off()
```

## ICD-10: barplot
```{r dev = "png"}
library('wesanderson')
library('ggplot2')
library('plotly')

icd_10 <- data %>% 
  dplyr::select(record_id, starts_with('ds_icd'), -ends_with('.factor')) %>%
  as.data.table %>%
  melt.data.table(id.vars = 'record_id', variable.name = "ds_icd", value.name = "illness_name") %>% 
  na.omit() %>% 
  as.data.frame %>%
  transform(illness_name = factor(illness_name,
                                  levels = c(1:19),
                                  labels = c("A00-B99", "C00-D48", "D50-D89", "E00-E90", "F00-F99", "G0-G99", "H00-H59", "H65-H75", "I00-I99", "J00-J99", "K00-K93", "L55-L59", "M00-M99", "N00-N99", "O00-O99", "Q00-Q99", "S00-T98", "V01-Y98", "Z00-Z13")))
  
#icd_10$illness_name <- as.factor(icd_10$illness_name)

icd_10.stat <- ggplot(data = icd_10, aes(x = illness_name), 
          position="dodge") +
          geom_bar(fill = wes_palette("Royal2")[5]) +
          xlab('Заболевания по МКБ-10') +
          ylab('Количество пациентов с данным заболеванием (по посещениям)') +
          theme(legend.position="left") +
          aes(stringr::str_wrap(illness_name, 15)) + xlab(NULL) +
          theme_minimal() +
          coord_flip()
          
ggplotly(icd_10.stat)

icd_10.stat
```

## ICD-10 vs homeless
```{r fig.width=6, fig.height=6, warning = F, message =F}
data %>%
  dplyr::select(record_id, Homeless, starts_with('ds_')) %>%
  dplyr::select(-ends_with('.factor')) %>%
  as.data.table %>%
  melt.data.table(id.vars = c('record_id', 'Homeless')) %>%
  dplyr::mutate(value = as.factor(case_when(value == 1 ~ 'A00-B99',
                                            value == 2 ~ 'C00-D48',
                                            value == 3 ~ 'D50-D89',
                                            value == 4 ~ 'E00-E90',
                                            value == 5 ~ 'F00-F99',
                                            value == 6 ~ 'G00-G99',
                                            value == 7 ~ 'H00-H59',
                                            value == 8 ~ 'H60-H95',
                                            value == 9 ~ 'I00-I99',
                                            value == 10 ~ 'J00-J99',
                                            value == 11 ~ 'K00-K93',
                                            value == 12 ~ 'L00-L99',
                                            value == 13 ~ 'M00-M99',
                                            value == 14 ~ 'N00-N99',
                                            value == 15 ~ 'O00-O99',
                                            value == 16 ~ 'Q00-Q99',
                                            value == 17 ~ 'S00-T98',
                                            value == 18 ~ 'V01-Y98',
                                            value == 19 ~ 'Z00-Z99') ) ) %>%
  dplyr::group_by(Homeless) %>%
  dplyr::summarise(icd10 = names(table(value)),
                   Count = table(value)
                   ) %>%
  dplyr::mutate(Homeless = factor(Homeless,
                                  levels = c('уличный', 'условно уличный',
                                             'домашний', 'Нет данных'))) %>%
  # Plot
  ggplot(aes(fct_reorder(icd10, Count,.desc = T), Count)) +
  facet_grid(rows = vars(Homeless)) +
  geom_bar(stat = 'identity', fill = wes_palettes$Rushmore1[3]) + 
  theme_bw() +
  labs(x = 'ICD-10', y = 'Observations') + 
  theme(axis.title = element_text(face = 'bold', size = 14),
        legend.title = element_text(face = 'bold', size = 14),
        axis.text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, vjust = 0.6),
        legend.text = element_text(size = 12))
  

```

# Shiny
## Plot quant vs quant
```{r fig.width=10, fig.height=7}

plot_quant_vs_quant <- function(df, var1, var2, cor.method = 'pearson', dropNA = F){
  # Specify main vars:
  colors.vars <- wes_palettes$Zissou1[c(1,5)]
  # Rename 
  df %<>%
    dplyr::rename('var1' = !!var1, 'var2' = !!var2) %>%
    { `if`(dropNA, na.omit(.), .)}
  
  
  # Basic stats
  ggStats <-
    df %>%
      dplyr::select(var1, var2) %>%
      # setNames(c(var1, var2)) %>%
      summary %>%
      tableGrob()
  
  # Plot distributions
  ggBox1 <- 
    df %>%  
    ggplot(aes(var1)) +
            geom_boxplot(fill = colors.vars[1])
  ggBox2 <- 
    df %>%  
    ggplot(aes(var2)) +
            geom_boxplot(fill = colors.vars[2])
  
  
  # Scatter plot
  ggScatter <-
    df %>%
      # Plot
      ggplot(aes(var1, var2)) +
          geom_point() +
          geom_smooth(method = 'lm') +
          stat_cor(method = cor.method, label.y.npc="top", label.x.npc = "left") +
          labs(caption = paste0('var1: ', var1,'\n',
                                  'var2: ', var2))
  
  return(grid.arrange(ggBox1, ggStats, ggBox2, ggScatter, nrow = 2, ncol = 2))
}


var1 = 'age.actual'
var2 = 'ch_ds.number'
data_done %>%
  plot_quant_vs_quant(var1 , var2, cor.method = 'spearman', dropNA = T)
```

## Plot factor vs factor
```{r fig.width=6, fig.height=6}
# Function for ordinal encoding
encode_ordinal <- function(x, order = sort(unique(x))) {
  x <- as.numeric(factor(x, levels = order, exclude = NULL))
  as.factor(x)
}

plot_factor_vs_factor <- function(df.raw, var1, var2, dropNA = F, original.names = T){
  # Specify main vars:
  colors.vars <- wes_palettes$Zissou1[c(1,5)]
  # Rename 
  df.raw %<>%
    dplyr::rename('var1' = !!var1, 'var2' = !!var2) %>%
    { `if`(dropNA, na.omit(.), .)}
  # Encode if needed
  if(!original.names){
    df <- df.raw %>% dplyr::mutate_all(encode_ordinal)
  }else {
    df <- df.raw
  }
    
  # Basic stats
  ggStats <-
    df %>%
      dplyr::select(var1, var2) %>%
      # Plot
      ggplot() +
        geom_mosaic(aes(x = product(var1, var2)), fill = colors.vars[1]) +
        geom_mosaic_text(aes(x = product(var1, var2), label = after_stat(.wt)), as.label=TRUE) +
        {if(!original.names) labs(caption = paste0('var1: ', var1,': \n', 
                      paste(paste0(sort(unique(encode_ordinal(df.raw$var1))), ' - ', sort(unique(df.raw$var1))), 
                            collapse = '\n'),
                      '\n\n',
                      'var2: ', var2,': \n',
                      paste(paste0(sort(unique(encode_ordinal(df.raw$var2))), ' - ', sort(unique(df.raw$var2))),
                            collapse = '\n')))
          } +
        {if(original.names) labs(x = var2, y = var1)} +
        theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5),
              plot.caption = element_text(size = 10))
    
  grid.arrange(ggStats)
}

var1 = 'nicotin.factor'
var2 =  'alcogolic.factor'
plot_factor_vs_factor(data_done, var1, var2, 
                      dropNA = T, 
                      original.names = T) #TODO convert all to NA or all to No anwser
```

## Plot quant vs factor
```{r fig.width=10, fig.height=5}
extract_all_comparisons <- function(.tbl) {
  .tbl %>%
    dplyr::select(.data$group1, .data$group2) %>%
    purrr::transpose() %>%
    purrr::modify_depth(1, unlist)
}

plot_quant_vs_factor <- function(df.raw, var1, var2, 
                                 dropNA = F, original.names = T,
                                 compare_mean_method = 't.test'){
  # Specify main vars:
  colors.vars <- wes_palettes$Zissou1[c(1,5)]
  # Figure out what var is factor
  if(is.factor(df.raw[[var1]]) | is.character(df.raw[[var1]])) {
    var.factor = var1
    var.quant = var2
  }else{
    var.quant = var1
    var.factor = var2
  }
  # Rename 
  df.raw %<>%
    dplyr::rename('var.quant' = !!var.quant, 'var.factor' = !!var.factor) %>%
    { `if`(dropNA, na.omit(.), .)}
  
  # Encode if needed
  if(!original.names){
    df <- df.raw %>% dplyr::mutate(var.factor = encode_ordinal(var.factor))
  }else {
    df <- df.raw
  }
  
  # Basic stats
  ggStats <-
    df %>%
      dplyr::select(var.quant, var.factor) %>%
      {`if`(original.names, setNames(., c(var.quant, var.factor)), .)} %>%
      summary %>%
      tableGrob()
  
  # Plot box
  # Calculate combinations of factors
  combinations = lapply(combn(na.omit(unique(df$var.factor)), 2, simplify = F), 
                        as.character)
  
  # ggBox <-
    df %>%  
    ggplot(aes(y= var.quant, x = var.factor, fill = var.factor)) +
            geom_boxplot() +
            geom_jitter(alpha = 0.2, width = 0.05) +
            stat_compare_means(aes(x = var.factor, y = var.quant, label = ..p.adj..),
                               method = compare_mean_method, 
                               comparisons = combinations,
                               na.rm = T) +
            # Appearance
            theme(axis.ticks.x = element_blank(),
                    axis.text.x = element_blank()) +
            {if(!original.names) labs(caption = paste0(
              'var.quant: ', var.quant, '\n\n',
              'var.factor: ', var.factor, '\n', # Add info if encoded
              paste(paste0(sort(unique(encode_ordinal(df.raw$var.factor))), ' - ',
                           sort(unique(df.raw$var.factor))), collapse = '\n')
              ))
            } +
            {if(original.names) labs(x = var.factor,
                                     y = var.quant,
                                     fill = var.factor)} # Add original names
  
  # return(grid.arrange(ggStats, ggBox, ncol = 2))
}

var1 = 'age.actual'
var2 = 'alcogolic.factor'
plot_quant_vs_factor(data_done, 
                     var1, var2, 
                     dropNA = T, 
                     original.names = F,
                     compare_mean_method = 't.test')
```

# Social factors
## education
```{r}
get_one_var_hist(data, var='education.factor', out_dir='plots',
                 xtitle='Образование', pall_values=c(wes_palettes$Rushmore1, wes_palettes$GrandBudapest1),
                 height = 3.5, width = 8, ratio=0.5)
```

## family
```{r}
get_one_var_hist(data,
                 var='family.factor', out_dir='plots',
                 xtitle='Семейное положение', pall_values=c(wes_palettes$Rushmore1),
                 height = 6, width = 8, ratio=0.8)
```


## Shiny
```{r}
ui <-  fluidPage(
  
  titlePanel(h1("Charity Hospital Project")),
  
  sidebarLayout(
      sidebarPanel(h1("Choosing variables", align = 'center'),
                    
                  selectInput("var1", label = h3("Select first variable"), 
                              choices = selected_vars, 
                              selected = 1),
                  
                  selectInput("var2", label = h3("Select second variable"), 
                              choices = selected_vars, 
                              selected = 1),
                  
                  selectInput("dropNA", label = h3("Drop NA or not?"), 
                              choices = c(T, F), 
                              selected = 1),
                  
                  selectInput("original.names", label = h3("Original names?"),
                              choices = c(T, F),
                              selected = 1),
                  
                  selectInput("means.method", label = h3("Which test use to compare means?"), 
                              choices = c('wilcox.test', 't.test'), 
                              selected = 1),
                  
                  selectInput("cor.method", label = h3("Which correlation test to use?"), 
                              choices = c('spearman', 'pearson'), 
                              selected = 1)
                  ),
      
      mainPanel(h1("Plots", align = 'center'),
                plotOutput(outputId = "plot"))
  )
  
)

server <- function(input, output) {
  
  output$plot <- renderPlot({
    
    vars = c(input$var1, input$var2)
    
    if(is.factor(data_done[[vars[1]]]) & is.factor(data_done[[vars[2]]])){
      # if both are factors
      return(plot_factor_vs_factor(data_done, vars[1], vars[2], 
                                   dropNA = input$dropNA,
                                   original.names = T
                                   ))
    }

    if((is.numeric(data_done[[vars[1]]]) & is.factor(data_done[[vars[2]]])) | 
       is.factor(data_done[[vars[2]]]) & is.factor(data_done[[vars[1]]])){
       # if factor vs quant
       return(plot_quant_vs_factor(data_done, vars[1], vars[2],
                         dropNA = input$dropNA,  
                         original.names = T,
                         compare_mean_method = input$means.method))
    }
    
    if(is.numeric(data_done[[vars[1]]]) & is.numeric(data_done[[vars[2]]])){
      # if both are factors
      return(plot_quant_vs_quant(data_done, vars[1], vars[2],
                                 dropNA = input$dropNA,
                                 cor.method = input$cor.method))
    }
    
    })
    
    
  
}

# Run the app ----
shinyApp(ui = ui, server = server)
```